The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-04 outputs/docs/events/paper.Rmd
Start states polarisation paper

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, and Chris Cochrane for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time. Finally, we consider the effect of various events using Bayesian hierarchical Dirichlet regression. We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on the short-term."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions. **Version as of**: `r format(Sys.time(), '%d %B %Y')`; **comments welcome**: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first compile a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. We then use a structural text model to reduce the dimensionality of the text and to impose prior knowledge such as correlation between days and steady changes over time. Finally, we consider the effect of various events using Bayesian hierarchical Dirichlet regression. We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on the short-term."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---
